Kelompok 4_Praktikum_Pekan 8

### 2024-04-07 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

plot_distribution <- function(data, title, color) {
  df <- data.frame(x = data)
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 0.7) +
    geom_density(aes(y = ..count..), fill = color, alpha = 0.4) + # Poligon densitas
    labs(title = paste("Histogram", title)) +
    theme_minimal()

  p2 <- ggplot(data = df, aes(sample = x)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste("Normal QQ Plot", title)) +
    theme_minimal()

@@

  colors <- c("blue", "green", "orange")  # warna yang berbeda untuk setiap jenis mixed data

@@

s

>>>>

plot_distribution <- function(data, title, color) {
  df <- data.frame(x = data)
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, alpha = 1) +
    geom_density(aes(y = ..count..), fill = color, alpha = 0.4) + # Poligon densitas
    labs(title = paste("Histogram", title)) +
    theme_minimal()

  p2 <- ggplot(data = df, aes(sample = x)) +
    stat_qq(color = color, size =5) +
    stat_qq_line(color = "red", linewidth =2) +
    labs(title = paste("Normal QQ Plot", title)) +
    theme_minimal()

@@

  colors <- c("#4664AF", "#9F4274", "#66C8CC")  # warna yang berbeda untuk setiap jenis mixed data

@@
